% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2015-2018 Serge Nevsky <sergey@sergeyk.com> http://snevsky.com
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{10in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{0pt}}
\newcommand{\resheading}[1]{\vspace{0pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-2pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Serge Nevsky} & \textbf{\today} \\
\texttt{serge@snevsky.com} & \texttt{www.snevsky.com} \\

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Employment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item 
  \ressubheading{Meta / Facebook}{Remote from Leawood, KS}{Lead Software Engineer}{July 2021 - Present}
    \begin{itemize}
        \resitem {
          Develop the Instagram and Facebook applications across iOS, Android and Web.
        }
        \resitem {
           Support critical company metrics. Develop frameworks to achieve the highest industry standards for metrics accuracy.
        }
        \resitem {
          iOS mobile development in Objective C and Swift. Android development in Kotlin and Java.
        }
        \resitem {
          Server side development in Hack (PHP), Python and C.
        }
	\end{itemize}


\item 
  \ressubheading{Cox Automotive / VinSolutions}{Mission, KS}{Lead Software Engineer}{October 2017 - June 2021}
    \begin{itemize}
        \resitem {
            Lead a development team through building, maintaining and designing features for an industry leading CRM application.
        }
        \resitem{
            Collaborated with product, engineering, architecture and leadership to present valuable solutions to long term projects and immediate concerns.
        }
        \resitem{
            Design stable, secure and scalable Distributed Systems in AWS and on-premise hardware. Developed and promoted learned patterns in the organization.
        }
        \resitem{
            Designed and implemented Disaster Recovery strategy across all teams. Received quarterly Engineering award for effort.
        }
        \resitem{
            Successfully merged two development teams with nearly 100 owned services. Received a quarterly Engineering award for this as well.
        }
        \resitem{
            Achieved exceptional level of quality for the development team, with zero reported production issues in all of 2020.
        }
        \resitem{
            Developed and regularly taught highly rated all-day course on Distributed Systems. Made into a requirement for all levels in engineering.
        }
        \resitem{
            Led a major engineering effort to decouple a piece of legacy functionality cross-organization.
        }
        \resitem{
            Used pub/sub messaging and queuing patterns for resiliency, scalability and availability.
        }
        \resitem{
            Built serverless Docker micro services running in AWS ECS and Fargate.
        }
        \resitem{
            Developed an automated testing framework for test engineers and introduced rollback upon test failure into deployment pipeline.
        }
        \resitem{
            Mentored team members daily through code reviews, 1 on 1s and strong foundation of trust.
        }
        \resitem{
            Actively promoted a culture of excellence in the organization by sharing experience through presentations and documentation.
        }
        \resitem{
            ASP.NET Core Web API back-end, React front-end and SQL Server database.
        }
	\end{itemize}

\item 
  \ressubheading{Site 1001}{Kansas City, MO}{Senior Software Development Engineer}{October 2016 - October 2017}
	\begin{itemize}
        \resitem{
            Build and maintain a data-driven facility management application
            aspiring to incorporate AI, Machine Learning and IoT technology.
        }
        \resitem{
            MVC Web Application with Entity Framework, RESTful Web API, Microsoft SQL Server.
        }
        \resitem{
            Client-side application utilized Razor syntax and component-based jQuery.
        }
        \resitem{
            Develop a Mobile application for iOS and Android using Xamarin.
        }
        \resitem{ 
            Design and implement architectural changes throughout all layers 
            of the application to improve performance and code quality while
            minimizing technical debt.
        }
        \resitem{
            Mentor and collaborate with a small team of developers in a 
            fast-paced development cycle. Design features and work with various
            lines of the company to iterate effectively.
        }
        \resitem{
            Developed Windows services to integrate with third party
            smart sensors and IoT devices.
        }
        \resitem{
            Upgraded enterprise application tools and dependencies: MVC2 to MVC5,
            .NET Framework 4 to .NET Framework 4.5.2, Web Forms views to Razor
            views and Visual Studio 2010 to 2017.
        }
	\end{itemize}

\item 
  \ressubheading{Bradford \& Galt / Heartland Crop Insurance}{Overland Park, 
    KS}{Software Engineer}{November 2015 - October 2016}
	\begin{itemize}
        \resitem{Design and support systems in a mathematically 
        intensive, enterprise level insurance application in .NET 
        using C\# 6.} 
        \resitem{Maintain stored procedures and views in Microsoft SQL 
        Server with NHibernate as the ORM.} 
        \resitem{Set up a specialized unit and regression testing 
        environment using NUnit.} 
	\end{itemize}

\item
	\ressubheading{Artisan Technology Group / Beyond the Scores}{Kansas City, MO}{Software 
    Engineer}{May 2015 - November 2015}
	\begin{itemize}
            \resitem{Develop an enterprise application as a 
            greenfield project from the ground up with a team of 
            mostly two developers. Involved in modeling, design,
            development and architecture.}
            \resitem{C\# .NET 4.5 Windows Presentation 
            Foundation (WPF) following the MVVM pattern.}
            \resitem{Communicate directly with clients on consulting 
            projects, supporting their products, developing new 
            features, and advising on architectural concerns.}
	\end{itemize}

\item
    \ressubheading{PeopleAdmin / Netchemia}{Prairie Village, KS}{Software 
    Engineer}{August 2013 - May 2015}
	\begin{itemize}
            \resitem{Develop features in C\# MVC and VB.NET Web Forms 
            products. Additional technologies 
            included Microsoft SQL Server, AngularJS, JQuery, 
            KnockoutJS and JavaScript.}
            \resitem{Product Owner, handling issue resolution, 
            delegating, testing, requirements and code 
            review.}
            \resitem{Work directly with an off-shore team to ensure 
            quality support for the product.}
            \resitem{Led a cross-organization team of seven to win the 
            first internal company hackathon, establishing a company 
            intranet.}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Rockhurst University}{Kansas City, MO}{B.A. in 
    Mathematics and French Language, Philosophy Minor}{2008 - 2012}
	\begin{itemize}
        \resitem{{\bf Rockhurst Outstanding Research Award} (2012)}
        \resitem{{\bf William A. Luby Mathematics Medal Award}}
        \resitem{Undergraduate research project published in \emph{Mathematical 
            Spectrum} \textbf{48}, 1, 22-29 (2014/2015) entitled \emph{Exploring the New 
        Zealand Puzzle}}
        \resitem{Competed in the Missouri Collegiate Mathematics 
        Competition}
        \resitem{Presented at CALHE Conference at Missouri Western 
        State University}
	\end{itemize}

\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

    \item {\bf Development}

        \begin{itemize}
            \resitem{\textbf{Mobile} \\ iOS (Swift, Objective C), Android (Kotlin, Java)}
            \resitem{\textbf{Microsoft} \\ C\#, Web API, MVC, Xamarin, WCF, VB.NET, WPF, ASP.NET, 
            Entity Framework, \\ .NET Core, Razor Pages, XAML, Web Forms, XML, PowerShell}
            \resitem{\textbf{Amazon} \\ Elastic Beanstalk, Elastic Container Service, Fargate, SQS, SNS, HashiCorp Terraform}
            \resitem{\textbf{Database} \\ Microsoft SQL Server, PostgreSQL, MongoDB, Presto, MySQL}
            \resitem{\textbf{Web} \\ JavaScript, ReactJS, TypeScript, jQuery, Node.js, Python, Hack (PHP)}
            \resitem{\textbf{Agile} \\ Scrum.org \textbf{Professional Scrum Master I} Certification, Kanban}
            \resitem{\textbf{Source Control} \\ Git, TFS, SVN, GitHub, SourceTree}
            \resitem{\textbf{Deployment} \\ AWS, Azure, Heroku, GitHub Pages, Octopus Deploy, Jenkins}
            \resitem{\textbf{*nix Technology} \\ \texttt{unix}, \texttt{vim}, \texttt{bash}, \texttt{zsh}, \texttt{screen}}
            \resitem{\textbf{Software} \\ Adobe Photoshop, Adobe Lightroom, WordPress}
        \end{itemize}

    \item {\bf Hobby}

      \begin{itemize}
          \resitem{\texttt{snevsky.com/projects}: Various personal programming projects.}
          \resitem{\texttt{snevsky.com/blog}: Personal blog, including technology topics.}
          \resitem{\texttt{snevsky.com/music}: Songwriting and music production.}
          \resitem{\texttt{snevsky.com/photography}: Digital photography.}
          \resitem{Collect and play many musical instruments.}
          \resitem{Text editor magic in \texttt{vim}.}
      \end{itemize}

    \item {\bf Language}

    \begin{itemize}
        \resitem{Fluent in English and Russian.}
        \resitem{Conversational in Telugu.}
        \resitem{Novice in French and Tamil.}
    \end{itemize}


%\item Hobbies include music production with Logic Pro X, visual design with Adobe InDesign and Photoshop, and text editor magic in vim.

\end{itemize}

\end{document}
